Digital History in Finland, 1488-1828

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, out.width="800px"}
df <- df0
df <- df %>%
        filter(catalog == "Fennica" & country == "Finland") %>%
        filter(publication_year >= 1640 & publication_year < 1828)

@@

>>>>

```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
df <- df0
df <- df %>%
        filter(catalog == "Fennica" & country == "Finland") %>%
        filter(publication_year >= 1640 & publication_year < 1828)

@@

```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# Title count
catalogue <- "Fennica"
place <- "Turku"

df <- df0
df <- df %>%
        filter(catalog == catalogue & publication_place == place) %>%
        filter(publication_year >= 1640 & publication_year < 1828)

df <- df %>%	
        select(publication_decade, publisher, paper.consumption.km2)

# Group small publishers
# Top publishers by title count
ntop <- 10
top <- names(top(df, "publisher", ntop))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, c(top, "Other"))

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally()

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publication_place)) +
       #geom_line(col = "black", aes(shape = publication_place)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +        
       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
print(p)

catalogue <- "Fennica"
place <- "Turku"

df <- df0
df <- df %>%
        filter(catalog == catalogue & publication_place == place) %>%
        filter(publication_year >= 1640 & publication_year < 1828)

df <- df %>%	
        select(publication_decade, publisher, paper.consumption.km2)

# Group small publishers
# Top publishers
ntop <- 5
top <- names(top(df, "publisher", ntop))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, c(top, "Other"))

# Publishing per decade & publisher	
npub <- df %>%
     	  group_by(publication_decade, publisher) %>%
	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
	  mutate(paper.per.title = paper/n)

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +        
       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
print(p)

# Paper consumption
catalogue <- "Fennica"
place <- "Turku"

df <- df0
df <- df %>%
        filter(catalog == catalogue & publication_place == place) %>%
        filter(publication_year >= 1640 & publication_year < 1828)

df <- df %>%	
        select(publication_decade, publisher, paper.consumption.km2)

# Group small publishers
# Top publishers by title count
ntop <- 10
top <- names(top(df, "publisher", ntop))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, c(top, "Other"))

# Publishing per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% summarize(paper = sum(paper.consumption.km2, na.rm = TRUE))

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publication_place)) +
       #geom_line(col = "black", aes(shape = publication_place)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Paper consumption") +        
       ggtitle(paste("Paper consumption per publisher (", place, "/", catalogue, ")", sep = ""))
print(p)

catalogue <- "Fennica"
place <- "Turku"

df <- df0
df <- df %>%
        filter(catalog == catalogue & publication_place == place) %>%
        filter(publication_year >= 1640 & publication_year < 1828)

df <- df %>%	
        select(publication_decade, publisher, paper.consumption.km2)

# Group small publishers
# Top publishers
ntop <- 5
top <- names(top(df, "publisher", ntop))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, c(top, "Other"))

# Publishing per decade & publisher	
npub <- df %>%
     	  group_by(publication_decade, publisher) %>%
	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
	  mutate(paper.per.title = paper/n)

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Paper") +        
       ggtitle(paste("Paper (", place, "/", catalogue, ")", sep = ""))
print(p)
